\input{./resume.header.tex}

\sodef\letterspacingbig{}{0.5pt}{.4em}{.4em}



\begin{document}
    \tabcolsep=0pt
    \tabulinesep=5pt
    \baselineskip=17pt
    \parskip=5pt
    \rmfamily\mdseries


    % ===========================
    % SECTIONS
    % ===========================
    \makeinfosection


    \begin{minipage}[t]{110mm}
        \mysection{CAREER HISTORY}

        \subsecexp{Product Principal}{GinkgoLeaf}{2021/03}{PRESENT}{
            \begin{compactitem}
                \item Managed ERP and OA system customization projects.
                \item Improved internal SOP.
            \end{compactitem}
        }

        \subsecexp{Product Principal}{Dimension}{2018/10}{2020/11}{
            \begin{compactitem}
                \item Managed Maskbook (privacy protection and more).
                \item Managed TesserPG (best mobile OpenPGP app).
                \item Co-managed agile development with the CTO.
                \item Managed branding for the corporation and the products.
            \end{compactitem}
            
            \myref{Learn more: dimension.im}
        }

        \subsecexp{Product Designer}{Zaoshu}{2016/10}{2017/08}{
            \begin{compactitem}
                \item Pushed the product design iterations in basic crawler scope.
                \item Pushed the introduction of advanced monitoring features.
                \item From feature brainstorming to visual design.
                \item Made exprience improvements.
            \end{compactitem}
        }

        \subsecexp{UX Designer}{Jisuanke}{2015/06}{2016/10}{
            \begin{compactitem}
                \item Maintained interaction design and visual design for the main product, online learning of programming.
                \item Participated branding and marketing.
            \end{compactitem}
        }
    \end{minipage}
    \hfill
    \begin{minipage}[t]{50mm}
        \raggedright

        \mysection{PROJECTS}

        \subsecproj{Product Manager}{Maskbook}
            {Post encrypted content on social media to avoid exploitation of big data and machine learning.
            Content types made richer.}
        \subsecproj{Product Manager}{TesserPG}
            {OpenPGP app for iOS and Android. The most welcomed OpenPGP app on App Store ever.
            Can interact with other apps as an input method.}
        \subsecproj{Product Manager}{DYBank}
            {Debt relation management system.}
        \subsecproj{Designer}{Kotomatsu}
            {Mysterious feline creature.}
        \subsecproj{Developer}{Archiviation}
            {Publish text files online over GitHub Pages but only visitors with certain share links can decrypt the contents.}
        
        \vspace{25pt}
        
        \footnotesize
        See GitHub for more projects.
    \end{minipage}




    % \begin{minipage}[t]{50mm}
    %     \mysection{SPECIALIZATION}\RaggedRight

    %     I especially like working on productivity tools.
    %     The famous verse "we make tools for these kind of people" still inspires me in this field.
    % \end{minipage}
    % \hfill
    % \begin{minipage}[t]{50mm}
    %     \mysection{LIFESTYLE}\RaggedRight

    %     I work with Gentoo, \LaTeX, VS Code, and other tools.
    %     With UX and frontend background, I love graphic design and typography.
    % \end{minipage}
    % \hfill
    % \begin{minipage}[t]{50mm}
    %     \mysection{EPILOGUE}\RaggedRight

    %     % Having three columns is a good idea, but what else content will be fitting? Let me know your suggestions.
    %     Follow my artwork drafts channel on Telegram at \underline{@neruthesartworkdrafts}.
    % \end{minipage}



    \vfill

    \begin{minipage}[t]{\textwidth}
        \footnotesize

        Copyright {\copyright} 2021 Neruthes.
        Made with \faIcon{heart} and {\LaTeX} on Gentoo Linux.
    \end{minipage}




\end{document}




